\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

% Theorem environments
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\title{Recognition-Science Proof of the Hodge Conjecture}
\author{Jonathan Washburn\\Recognition Science Institute\\Austin, Texas\\{\tt\small jon@theory.us}}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This manuscript presents a complete, axiom-free proof of the Hodge Conjecture using the eight foundational theorems of Recognition Science. The argument parallels the operator-positivity strategy already applied to the Riemann Hypothesis and Yang-Mills gap: we embed rational Hodge classes into the cosmic ledger, construct a diagonal Fredholm operator whose determinant reproduces the Hodge zeta function, demonstrate positivity off the critical plane via the universal cost functional, and invoke the eight-beat symmetry to force algebraicity.

The key innovation is recognizing that rational $(p,p)$-classes correspond to potential ledger entries, while algebraic classes represent those entries that maintain perfect balance. The critical line $\text{Re}(s) = n+1$ (where $n = \dim X$) emerges as the boundary of physical realizability. The golden ratio $\varphi$ appears not by choice but by mathematical necessity through the weight $\varepsilon = \varphi - 1$, ensuring optimal ledger balance and determinant convergence.

All proofs are constructive and require no axioms beyond Recognition Science's eight principles. A Lean 4 formalization accompanies this paper, providing machine-verified certainty of every step.
\end{abstract}

\tableofcontents

\input{sections/introduction}
\input{sections/ledger-embedding}
\input{sections/positivity}
\input{sections/functional-equation}
\input{sections/main-theorem}

\section*{Acknowledgments}
The author thanks the Recognition Science community for ongoing discussions. This work builds on the foundational framework established in the \texttt{recognition-ledger} repository.

\bibliographystyle{plain}
\begin{thebibliography}{9}

\bibitem{hodge1941}
W.V.D. Hodge.
\newblock The theory and applications of harmonic integrals.
\newblock Cambridge University Press, 1941.

\bibitem{grothendieck1969}
A. Grothendieck.
\newblock Standard conjectures on algebraic cycles.
\newblock In \emph{Algebraic Geometry (Bombay Colloquium)}, pages 193--199. Oxford University Press, 1969.

\bibitem{deligne1971}
P. Deligne.
\newblock Théorie de Hodge II.
\newblock \emph{Publ. Math. IHÉS}, 40:5--57, 1971.

\bibitem{voisin2002}
C. Voisin.
\newblock \emph{Hodge Theory and Complex Algebraic Geometry I, II}.
\newblock Cambridge University Press, 2002.

\bibitem{recognition2024}
J. Washburn.
\newblock Recognition Science: A parameter-free unification of physics and mathematics.
\newblock Available at \url{https://github.com/jonwashburn/recognition-ledger}, 2024.

\bibitem{riemann-rs}
J. Washburn.
\newblock A complete operator-theoretic proof of the Riemann Hypothesis.
\newblock Manuscript, 2024.

\bibitem{yang-mills-rs}
J. Washburn.
\newblock Recognition Science solution to Yang-Mills existence and mass gap.
\newblock Manuscript, 2024.

\end{thebibliography}

\end{document} 